%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Data Scientist} % Job title
    {Siren Analytics} % Organization
    {Beirut, Lebanon} % Location
    {Jan. 2021} % Date(s)
    {Worked on Anomaly Detection systems for lockdown mobility permits, Chatbots, and data analysis.}
%---------------------------------------------------------
  \cventry
    {AI Instructor } % Job title
    {Zaka} % Organization
    {Online} % Location
    {May. 2020 - Current} % Date(s)
    {Developed and delivered training on AI and ML topics including Natural Language Processing}
%---------------------------------------------------------

  \cventry
    {Machine Learning Expert} % Job title
    {Stars of Science} % Organization
    {Doha, Qatar} % Location
    {Feb. 2020 - Apr. 2020} % Date(s)
    {Provided ML and AI solutions to contestants as part of the support team\smallskip}


%---------------------------------------------------------


  \cventry
    {Graduate Research Assistant} % Job title
    {MIND Lab (Prof. Hazem Hajj) - American University of Beirut} % Organization
    {Beirut, Lebanon} % Location
    {Sep. 2018 - Current} % Date(s)
    {Research focuses on SOTA NLP technologies and social chatbots. }


%---------------------------------------------------------
  \cventry
    {Graduate Teaching Assistant} % Job title
    {ECE Dept. - American University of Beirut} % Organization
    {Beirut, Lebanon} % Location
    {Feb. 2018 - Dec. 2018} % Date(s)
    { 
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {EECE 435L: Software Tools Lab, Co-Instructor (3 semesters)}
        \item {EECE 696: Applied Parallel Programming, Lab instructor (1 semester)}
        \item {EECE 330: Data Structures and Algorithms, Lab instructor (1 semester)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {Huawei Technologies (Lebanon) S.A.R.L.} % Organization
    {Beirut, Lebanon} % Location
    {June 2016  - Aug. 2016} % Date(s)
    {}
    % {Learned about various LTE principles, base station hardware, and Microwave transmissions systems.}


%---------------------------------------------------------
\end{cventries}
